1. Original Data

### 2021-04-10 reports/0_generalIdea.Rmd
update report structure

---
title: "Gächter et al (2007, JPE) replication"
description: |
  Reproducing Gächter et al.'s Visualizations.
author:
  - name: Hauke Roggenkamp 
    affiliation: CLICCS
    affiliation_url: https://www.cliccs.uni-hamburg.de/
date: "`r Sys.Date()`"
bibliography: biblio.bib
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
    toc_float: false
    code_folding: true
---

@@

base::load(file = "../data/processed/simulations.rda") 
base::load(file = "../data/processed/demoSession.rda") 
base::load(file = "../data/processed/gaechter2017.rda") 
```

@@

In an attempt to incorporate uncertainty to @GACHTER2017's dynamic public goods game (DPGG), we plan to run a series of remote online experiments using oTree [@oTree]. One of these experiments will replicate Gächter et al.'s NOPUNISH 10-period version as close as possible (given the remote circumstances) to allow for comparisons.

@@

```{r combineData}
combined <- rbindlist(list(longDT[treatment == "Hi000"],# | treatment == "Lo000"], 
                           gaechter,
                           demoSession))

combined[treatment == "demoSession"] %>%
  # head(n = 9) %>%
  kbl() %>% 
  scroll_box(height = "400px") %>%
  kable_paper("hover", 
              full_width = TRUE,
              fixed_thead = TRUE)
```

@@

The following graph displays the zero risk treatments together with @GACHTER2017's data. The original ```noPunish10``` data lies between both sets of simulations.

@@

# plot
ggplot(data = plotDT, aes(x = round, y = temp, fill = treatment, color = treatment)) + 
    layout +
    scale_fill_manual(values = wes_palette("GrandBudapest1")) +
    scale_color_manual(values = wes_palette("GrandBudapest1")) +
    geom_errorbar(aes(ymin=temp-se, ymax=temp+se), width=.25, alpha = 0.5) +
    geom_line() +
    geom_point() + 
    scale_x_continuous(name="Period",  breaks = 1:15) +
    scale_y_continuous(expand = c(0, 0), limits = c(0, 1)) +
    labs(y = "Share of Current Endowment contributed")
```

@@

# plot
ggplot(data = plotDT, aes(x = round, y = temp, fill = treatment, color = treatment)) + 
    layout +
    scale_fill_manual(values = wes_palette("GrandBudapest1")) +
    scale_color_manual(values = wes_palette("GrandBudapest1")) +
    geom_errorbar(aes(ymin=temp-se, ymax=temp+se), width=.25, alpha = 0.5) +
    geom_line() +
    geom_point() + 
    scale_x_continuous(name="Period",  breaks = 1:15) +
    scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) +
    labs(y = "Average Amount of Points contributed")
```

@@

# plot
ggplot(data = plotDT, aes(x = round, y = temp, fill = treatment, color = treatment)) + 
    layout +
    scale_fill_manual(values = wes_palette("GrandBudapest1")) +
    scale_color_manual(values = wes_palette("GrandBudapest1")) +
    geom_errorbar(aes(ymin=temp-se, ymax=temp+se), width=.25, alpha = 0.5) +
    geom_line() +
    geom_point() + 
    scale_x_continuous(name="Period",  breaks = 1:15) +
    scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) +
    labs(y = "Wealth")
```

# Incorporating Risk or Uncertainty

>>>>

---
title: "Replicate and extend Gächter et al's (2007, JPE) dynamic public goods game"
description: |
  Draft.
author:
  - name: Hauke Roggenkamp 
    affiliation: CLICCS
    affiliation_url: https://www.cliccs.uni-hamburg.de/
  - name: Stefan Traub 
    affiliation: Helmut Schmidt University
    affiliation_url: https://www.hsu-hh.de/en/
  - name: Michael Berlemann 
    affiliation: Helmut Schmidt University
    affiliation_url: https://www.hsu-hh.de/en/
date: "`r Sys.Date()`"
bibliography: biblio.bib
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
    toc_float: false
    code_folding: true
---

@@

base::load(file = "../data/processed/rda/replication2021.rda") 
base::load(file = "../data/processed/rda/gaechter2017.rda") 
```

@@

In an attempt to incorporate uncertainty to @GACHTER2017's dynamic public goods game (DPGG), we plan to run a series of remote online experiments using oTree [@oTree]. One of these experiments will replicate Gächter et al.'s NOPUNISH 10-period version as close as possible (given the remote circumstances). The current demo version of the experiment can be found [here](https://cliccs.herokuapp.com/). Click [here](https://github.com/Howquez/coopUncertainty) to visit the corresponding Github repository.

This report first reproduces the main visualizations from the original paper using @GACHTER2017's data as well as data simulated by rather simple oTree bots. Afterwards, a very broad idea of an additional treatment is drafted.

@@

```{r combineData}
combined <- rbindlist(list(gaechter,
                           replication),
                      use.names = TRUE)

combined %>%
  # head(n = 9) %>%
  kbl() %>% 
  scroll_box(height = "400px") %>%
  kable_paper("hover", 
              full_width = TRUE,
              fixed_thead = TRUE)
```

@@

The following graphs display simulated data together with @GACHTER2017's data.

@@

# plot
ggplot(data = plotDT, aes(x = round, y = temp, fill = treatment, color = treatment)) + 
    layout +
    scale_fill_manual(values = wes_palette("GrandBudapest1")) +
    scale_color_manual(values = wes_palette("GrandBudapest1")) +
    geom_errorbar(aes(ymin=temp-se, ymax=temp+se), width=.25, alpha = 0.5) +
    geom_line() +
    geom_point() + 
    scale_y_continuous(expand = c(0, 0), limits = c(0, 1)) +
    labs(y = "Share of Current Endowment contributed", x = "Period")
```

@@

# plot
ggplot(data = plotDT, aes(x = round, y = temp, fill = treatment, color = treatment)) + 
    layout +
    scale_fill_manual(values = wes_palette("GrandBudapest1")) +
    scale_color_manual(values = wes_palette("GrandBudapest1")) +
    geom_errorbar(aes(ymin=temp-se, ymax=temp+se), width=.25, alpha = 0.5) +
    geom_line() +
    geom_point() + 
    scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) +
    labs(y = "Average Amount of Points contributed", x = "Period")
```

@@

# plot
ggplot(data = plotDT, aes(x = round, y = temp, fill = treatment, color = treatment)) + 
    layout +
    scale_fill_manual(values = wes_palette("GrandBudapest1")) +
    scale_color_manual(values = wes_palette("GrandBudapest1")) +
    geom_errorbar(aes(ymin=temp-se, ymax=temp+se), width=.25, alpha = 0.5) +
    geom_line() +
    geom_point() + 
    scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) +
    labs(y = "Wealth", x = "Period")
```

Finally, the gini plot looks as follows:

```{r plotGini}
plotDT <- summarySE(data = combined, 
                      measurevar = "gini", 
                      groupvars=c("treatment", "round"),
                      na.rm = FALSE,
                      conf.interval = 0.95,
                      .drop = TRUE)

temp <- plotDT[, "gini"]

# plot
ggplot(data = plotDT, aes(x = round, y = temp, fill = treatment, color = treatment)) + 
    layout +
    scale_fill_manual(values = wes_palette("GrandBudapest1")) +
    scale_color_manual(values = wes_palette("GrandBudapest1")) +
    geom_errorbar(aes(ymin=temp-se, ymax=temp+se), width=.25, alpha = 0.5) +
    geom_line() +
    geom_point() + 
    scale_y_continuous(expand = c(0, 0), limits = c(0, 1)) +
    labs(y = "Wealth", x = "Period")
```

# Incorporating Extreme Weather Events

### 2021-04-10 reports/_legacy/equilibria.Rmd
update report structure

We'll therefore run sessions with groups of four ($i \in I=\{1,2,3,4\}$), an initial endowment of $N_i^1 = 20$ points $T=10$ rounds, a private account with a return of $1$ and a group account with a return of $1.5$ ($\Rightarrow$ MPCR$\equiv \frac{1.5}{4}$), such that:
$$
N_i^{t+1}=N_i^t - c_i^t + \frac{1.5}{4}\sum_{j=1}^4 c_j^t
$$
**Proposition 1:** Consider the public good game with growth as defined above. The unique SPE of the game is such that all players contribute 0 throughout the entire game (both on and off the equilibrium path).^[See @GACHTER2017's Appendix for a formal proof.]

@@

The basic idea is that, in every period, there is a (known or unknown)^[TBD] constant probability of an extreme weather event occurring in a group denoted by $r \equiv \frac{5}{16}=31.25$%. Such an extreme weather event can bring about damage $D$. This damage will, however, only occur if the group's contributions are smaller than a threshold $X$, which is half of their endowment, i.e. if:

@@

$$
N_i^t=
\begin{cases}
N_i^t - c_i^t + \frac{1.5}{4}\sum_{j=1}^4 c_j^t, & \text{if}\ \sum_{j=1}^4 c_j^t \geq \frac{1}{2} \sum_{j=1}^4 E_j^t\\
N_i^t - c_i^t + \frac{1.5}{4}\sum_{j=1}^4 c_j^t -rD, & \text{else}
\end{cases}
$$

With $D=0$ the game collapses to @GACHTER2017's model. The first derivative yields $-1$ implying that the individually rational contribution $c_{FC}^t=0$. 
If $A=4$ denotes the number of players and $C^t$ the aggregate contribution with $C^t=\sum_{j=1}^{A}c_j^t$, the aggregate payoff with $D=0$ is described by:

\begin{align}
\sum_{j=1}^{A}N_j^{t+1} & =\sum_{j=1}^{A}N_j^t - C^t + A \cdot \frac{1.5}{4} \cdot C^t\\
&=\sum_{j=1}^{A}N_j^t + C^t(4 \cdot \frac{1.5}{4} - 1) \\
&=\sum_{j=1}^{A}N_j^t + \frac{C^t}{2}
\end{align}

The collectively rational (that is, the efficient) contribution is $C_{FC}^t=\sum_{j=1}^{A}N_j^t$ because the first derivative is strictly positive.

As a consequence, the game is a dilemma where the individual and collective interest are in conflict.

Incorporating $D>0$, we want the game to remain a dilemma in which and observe whether positive contributions evolve despite contrasting incentives. As a consequence, we have to set $D$ such that freeriding ($c_i^t=0$ for all $i$) and risking to suffer that damage (LHS) remains more attractive than any contribution ($\bar c^t \geq \frac{\bar{N}^t}{2}$) that leads to damage control (RHS).

\begin{align}
N_i^t rD &> N_i^t - \bar{c}^t + A \cdot \frac{1.5}{4} \bar{c}^t \\
N_i^t (rD-1) &> \frac{\bar{c}^t}{2}
\end{align}

## The last period

@@

But what is the best thing to do in those cases, where $i$'s contribution can make a difference in damage control, that is, where $\sum_{j \neq i}^4 c_j^t < X < \sum_{j \neq i}^4 c_j^t + E_i^t$? In these cases, $i$ can contribute anything in  between $0 \leq c_i^t \leq X-\sum_{j \neq i}^4 c_j^t$ (the upper limit is the bare minimum required to prevent damages.

But how much is $i$ actually willing to contribute? $i$ will contribute as long as her earnings from these contributions with successful damage control (LHS) are larger than her reduced earnings from $c_i^t=0$ with expected damage (RHS).

\begin{align}
N_i^t - c_i^t + \frac{1.5}{4}\sum_{j=1}^4 c_j^t & \geq 
 N_i^t + \frac{1.5}{4}\sum_{j=1}^4 c_j^t-rD\\

N_i^t - c_i^t \Big(1-\frac{1.5}{4}\Big) + \frac{1.5}{4}\sum_{j\neq i}^4 c_j^t & \geq 
 N_i^t + \frac{1.5}{4}\sum_{j\neq i}^4 c_j^t-rD\\

- c_i^t\Big(1-\frac{1.5}{4}\Big) & \geq -rD\\

c_i^t & \leq \frac{rD}{1-\frac{1.5}{4}}\\

c_i^t & \leq \frac{D}{2} \; \text{ with }r=\frac{5}{16}\\ 
\end{align}

There are two things to note. First and unsurprisingly, the maximal contribution increases in risk and Damage. Second and given the MPCR and the (indeed artificial) risk level, the maximum amount any player would contribute is half the damage they would have suffered due to an extreme weather event if they had not reached the threshold. It is important to remember that they only make that contribution if their contribution is pivotal in controlling the damage.

Because the game is symmetrical and because it requires every player to contribute at least half of her endowment to control the damage, there is a Nash equilibrium where each player contributes $c_i^t = \frac{1}{2} N_i^t$ if $D_i^t \geq N_i^t$.

If players cannot make any debt (limited liability), the damage cannot be larger than their endowment. In that case, the players are indifferent in contributing nothing or exactly half of their endowments. If the risk was larger than $31.25$%, positive contributions (that is $c_i^t = \frac{1}{2} N_i^t$) become more likely in the last round.

>>>>

We'll therefore run sessions with groups of four ($i \in I=\{1,2,3,4\}$), an initial endowment of $N_i^1 = 20$ points $T=10$ rounds, a private account with a return of $1$ and a group account with a return of $1.5$ ($\Rightarrow$ MPCR$\equiv \frac{1.5}{4}$), such that:
$$
N_i^{t+1}=N_i^t - c_i^t + \frac{1.5}{4}\sum_{j=1}^4 c_j^t
$$
**Proposition 1:** Consider the public good game with growth as defined above. The unique SPE of both the game without punishment and with punishment is such that all players contribute 0 throughout the entire game (both on and off the equilibrium path).^[See @GACHTER2017's Appendix for a formal proof.]

@@

The basic idea is that, in every period, there is a (known or unknown)^[TBD] constant probability of an extreme weather event occurring in a group denoted by $r \equiv \frac{1}{3}$. Such an extreme weather event can bring about damage (denoted as $d\equiv\frac{1}{2}$), i.e. cut each group member's earnings $N_i^{t+1}$ in half. This damage will, however, only occur if the group's contributions are smaller than a threshold $X$, which is half of their endowment, i.e. if:

@@

$$
\mathbb{E}\big[N_i^t\big]=
\begin{cases}
N_i^t - c_i^t + \frac{1.5}{4}\sum_{j=1}^4 c_j^t, & \text{if}\ \sum_{j=1}^4 c_j^t \geq \frac{1}{2} \sum_{j=1}^4 E_j^t\\
\Big(N_i^t - c_i^t + \frac{1.5}{4}\sum_{j=1}^4 c_j^t\Big) \Big(1-r(1-d)\Big), & \text{else}
\end{cases}
$$

with $\Big(1-r(1-d)\Big)=\frac{5}{6}$ in our setting.

## The last period without inequality

Let's consider the artificial case of risk neutral players and symmetric endowments during the last period to dive deeper into the players' strategic environment. What is the best response $c_i \in BR_i(c_{-i})$, i.e. the optimal contribution of $i$ given the contributions of all $j \neq i$?

@@

But what is the best thing to do in those cases, where $i$'s contribution can make a difference in damage control, that is, where $\sum_{j \neq i}^4 c_j^t < X < \sum_{j \neq i}^4 c_j^t + E_i^t$? In these cases, $i$ will either contribute nothing ($c_i^t=0$) or the bare minimum to prevent expected damages ($c_i^t= X-\sum_{j \neq i}^4 c_j^t$).

$i$ will contribute as long as her earnings from these contributions with successful damage control (LHS) are larger than her reduced earnings with damage (RHS).

\begin{align*}
N_i^t - c_i^t + \frac{1.5}{4}\sum_{j=1}^4 c_j^t & \geq 
 \Big(1-r(1-d)\Big)\Big(N_i^t + \frac{1.5}{4}\sum_{j=1}^4 c_j^t\Big)\\

N_i^t - c_i^t(1-\frac{1.5}{4}) + \frac{1.5}{4}\sum_{j\neq i}^4 c_j^t & \geq 
 \Big(1-r(1-d)\Big) \Big(N_i^t + \frac{1.5}{4}\sum_{j\neq i}^4 c_j^t\Big)\\

-c_i^t(1-\frac{1.5}{4}) & \geq 
\Big(-r(1-d)\Big) \Big(N_i^t + \frac{1.5}{4}\sum_{j\neq i}^4 c_j^t\Big)\\

c_i^t & \leq \frac{r(d-1)}{\frac{1.5}{4} - 1} \Big(N_i^t + \frac{1.5}{4}\sum_{j\neq i}^4 c_j^t\Big)\\

c_i^t & \leq \frac{8}{30} N_i^t + \frac{1}{10}\sum_{j\neq i}^4 c_j^t\\

\end{align*}

Given the others' contributions, $c_i^t$ depends on the income $i$ would lose if the group fails to control the damage (and the fixed parameters $r$, $d$ as well as the MPCR).

Because this is a symmetric game (by assumption), we can set $c_i^t=c_j^t=c^t$ and find that the maximal contribution players would be willing to make falls short the threshold:

\begin{align*}
c^t & = \frac{8}{30} N^t + \frac{3}{10} c^t\\
\frac{7}{10}c^t & = \frac{8}{30} N^t\\
c^t & = \frac{8}{21} N^t < \frac{N^t}{2}\\
\Rightarrow c^* & = 0
\end{align*}

Because each individual's maximum contribution is smaller than half of her Endowment, the extreme weather event's damage is inevitable. As a consequence, the individuals do not contribute in the first place.

## The last period with inequality

(How) does this change if endowments are heterogeneous?

## Any period with inequality

...

### 2021-04-10 reports/a_originalData.Rmd
update report structure

library(haven)
library(data.table)
library(magrittr)
library(kableExtra)
library(DescTools) # gini coefficient
library(downloadthis)
library(Rmisc)
library(ggplot2)
library(wesanderson)

DT <- read_dta(file="../data/gaechteretal/GMTV-data.dta") %>% data.table()
```

@@

# Original Data

The data can be found in the supplementary materials they provide in their [online appendix](https://www.sciencedirect.com/science/article/pii/S0047272717300361#s0115).

```{r data, include = FALSE}
noPunish10 <- DT[exp_num == 5 | exp_num == 8 | exp_num == 9]
```

Within the appendix, one also learns that the NOPUNISH 10-period data were collected in sessions 5, 8 and 9. Subsetting the data correspondingly yields a ```data.table``` consisting of 23 observations and $4 \times 10 \times 23=$ `r NROW(noPunish10)` rows and 27 variables.

For this purpose only a few variables are relevant:

- ```exp_num``` is a session identifier
- ```per``` denotes the period
- ```gr_id``` is a group identifier (carrying treatment information)
- ```subj_id``` is a subject identifier
- ```tokens``` reports a subject's endowment in a period
- ```other[1-3]``` report the other group members' endowments in a period
- ```gdp ``` equals the sum of endowments of a group in a period
- ```putin``` reports a subject's contribution in a period
- ```pu[1-3]``` report the other group members' contributions in a period
- ```sum``` equals the sum of contributions of a group in a period.
- ```gini``` reports a group's Gini coefficient in a period.
- ```mean``` reports the fraction of sum/gdp -- but only in some cases.

As a consequence, the first few rows of the data look as follows:

```{r showData, layout = "l-body-outset"}
noPunish10[,
           gini2 := Gini(c(tokens, other1, other2, other3)),
           by = .(subj_id, per)]

noPunish10[order(gr_id, per),
           .(exp_num, gr_id, per, subj_id, # IDs
             tokens, other1, other2, other3, gdp, #endowments
             putin, pu1, pu2, pu3, sum, mean, # contributions
             gini, gini2
           )] %>% 
  head(n = 15) %>%
  kbl() %>% 
  # scroll_box(height = "200px") %>%
  kable_paper("hover", 
              full_width = TRUE,
              fixed_thead = TRUE)

```

We see group 501 in the first two periods where subjects 511 to 514 start with an initial endowment of 20 which makes a GDP of 80. Subject 511 does not contribute (as represented in ```putin==0``` in the first row and ```pu1==0```in rows 2 to 4) while the others contribute 5, 15 and 15 in the first period, respectively. The ```sum``` of contributions therefore equals 35 period 1.

With a sum of contributions being 35 and a return of contributions of 1.5, each subject receives ```ceil(13.125)``` =14 points from the group project such that the next period's ```gdp``` equals 101.

Unfortunately, the Gini coefficient (```gini```) is a little off as one can see in the second period: Even though this is a group level variable, the group has three different coefficient in the same period. For this reason, I re-calculated the coefficient and called it ```gini2```.

# Data Manipulation

To resemble the oTree data, the original data has to be transformed a little. Therefore, some variables will be renamed, variables (such as ```stock```^[Gächter et al. called this variable _Wealth_] and ```gain```) will be created and, most notably, the unit of observations will be groups such that subject-level variables will be dropped.^[In addition, I will ignore the original Gini coefficient and use mine instead.]

```{r writeData}

noPunish10[,
           share := sum/gdp,
           by = .(subj_id, per)]

gaechter <- noPunish10[order(gr_id, per),
           .(treatment = "noPunish10", 
             session.code = exp_num,
             groupID = gr_id, 
             round = per,
             contribution = sum,
             endowment = gdp,
             share = mean, # share,
             stock = (gdp + ceiling(sum/4*1.5)*4-sum),
             gain = (ceiling(sum/4*1.5)*4-sum),
             gini = gini2,
             bot_active = 0,
             # disaster = 0,
             # EWE = 0,
             noComprehension = 0)] %>% unique()

gaechter %>%
  head(n = 15) %>%
  kbl() %>% 
  kable_paper("hover", 
              full_width = TRUE,
              fixed_thead = TRUE)

save(gaechter, file = "../data/processed/rda/gaechter2017.rda")
write.csv(gaechter, file ="../data/processed/csv/gaechter2017.csv")

```

```{r downloadData}
gaechter %>%
      download_this(
        output_name = "Gaechter2017noPunish10",
        output_extension = ".csv", # CSV output
        button_label = "Download csv",
        button_type = "default"
        )
```

# Visualizations

```{r}
layout <- theme(panel.background = element_rect(fill = "white"),
                panel.grid = element_line(colour="gray", size=0),
                panel.grid.major.y = element_line(colour="gray", size=0.25),
                legend.key = element_rect(fill = "white"),
                axis.line.x.bottom = element_line(size = 0.25),
                axis.line.y.left = element_line(size = 0.25),
                plot.margin = unit(c(1,1,1,1), "cm"),
                legend.title = element_blank()
                )
```

```{r plotContribution}
plotDT <- summarySE(data = gaechter, 
                      measurevar = "contribution", 
                      groupvars=c("treatment", "round"),
                      na.rm = FALSE,
                      conf.interval = 0.95,
                      .drop = TRUE)

temp <- plotDT[, "contribution"]

# plot
ggplot(data = plotDT, aes(x = round, y = temp, fill = treatment, color = treatment)) + 
    layout +
    geom_errorbar(aes(ymin=temp-ci, ymax=temp+ci), width=.25, alpha = 0.5) +
    geom_line() +
    geom_point() + 
    scale_x_continuous(name="Period",  breaks = 1:15) +
    scale_y_continuous(expand = c(0, 0), limits = c(0, 150)) +
    labs(y = "Average Amount of Points contributed") +
    scale_color_manual(values = wes_palette("Moonrise3"))
```

```{r plotShare}
plotDT <- summarySE(data = gaechter, 
                      measurevar = "share", 
                      groupvars=c("treatment", "round"),
                      na.rm = FALSE,
                      conf.interval = 0.95,
                      .drop = TRUE)

temp <- plotDT[, "share"]

# plot
ggplot(data = plotDT, aes(x = round, y = temp, fill = treatment, color = treatment)) + 
    layout +
    geom_errorbar(aes(ymin=temp-ci, ymax=temp+ci), width=.25, alpha = 0.5) +
    geom_line() +
    geom_point() + 
    scale_x_continuous(name="Period",  breaks = 1:15) +
    scale_y_continuous(expand = c(0, 0), limits = c(0, 1)) +
    labs(y = "Share of Current Endowment contributed") +
    scale_color_manual(values = wes_palette("Moonrise3"))
```

```{r plotStock}
plotDT <- summarySE(data = gaechter, 
                      measurevar = "stock", 
                      groupvars=c("treatment", "round"),
                      na.rm = FALSE,
                      conf.interval = 0.95,
                      .drop = TRUE)

temp <- plotDT[, "stock"]

# plot
ggplot(data = plotDT, aes(x = round, y = temp, fill = treatment, color = treatment)) + 
    layout +
    geom_errorbar(aes(ymin=temp-ci, ymax=temp+ci), width=.25, alpha = 0.5) +
    geom_line() +
    geom_point() + 
    scale_x_continuous(name="Period",  breaks = 1:15) +
    scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) +
    labs(y = "Wealth") +
    scale_color_manual(values = wes_palette("Moonrise3"))
```

```{r plotGini}
plotDT <- summarySE(data = gaechter, 
                      measurevar = "gini", 
                      groupvars=c("treatment", "round"),
                      na.rm = FALSE,
                      conf.interval = 0.95,
                      .drop = TRUE)

temp <- plotDT[, "gini"]

# plot
ggplot(data = plotDT, aes(x = round, y = temp, fill = treatment, color = treatment)) + 
    layout +
    geom_errorbar(aes(ymin=temp-ci, ymax=temp+ci), width=.25, alpha = 0.5) +
    geom_line() +
    geom_point() + 
    scale_x_continuous(name="Period",  breaks = 1:15) +
    scale_y_continuous(expand = c(0, 0), limits = c(0, 0.4)) +
    labs(y = "Gini coefficient") +
    scale_color_manual(values = wes_palette("Moonrise3"))
```

# Tables

```{r regressions}
# reg gdp punish if longgame==0  & treat<3 & per==10, cluster(gr_id)
lm(gdp ~ punish, data = DT[longgame==0 & treat < 3 & per==10])
```

# Discussion

Even though the figures above were created using the original data, they do not look the same as the original figures. This becomes obvious if one looks at the figures that visualize the contributions. The arising question therefore is whether I made a mistake in processing and interpreting the data. After all I thought to have found wrong Gini coefficients and struggle to interpret the ```mean``` of the original data.

# First round

Eventually, we'll also be interested in the participants' first round's behavior, as it indicates their willingness to cooperate before they interact with one another. As a consequence, we can compare all noPunish sessions, regardless of whether they ran for 10 or 15 rounds.

```{r firstRound}
noPunish <- DT[exp_num == 1 | exp_num == 3 | # noPunish15
                 exp_num == 5 | exp_num == 8 | exp_num == 9] # noPunish10

temp <- noPunish[per == 1]
temp <- temp[,
             treatment := "noPunish10"]
temp <- temp[exp_num == 1 | exp_num == 3,
             treatment := "noPunish15"]

gaechterFirstRound <- temp[,
                           .(participant.code = subj_id,
                             treatment,
                             session.code = exp_num,
                             groupID = gr_id,
                             belief = NA,
                             othersContribution = sumputin - putin,
                             ownContribution = putin,
                             fairness = NA,
                             trust = NA,
                             comprehension = NA)]

rm(list = c("temp"))

# save data
fileName <- "gaechter2017"
save(gaechterFirstRound, 
     file = paste0("../data/processed/rda/", fileName, "_R1", ".rda"))
write.csv(gaechterFirstRound, 
          file = paste0("../data/processed/csv/", fileName, "_R1", ".csv"))
```

`r NROW(gaechterFirstRound)` participants yield `r NROW(gaechterFirstRound)` independent observations that are stored in a data table called ```gaechterFirstRound```. These observations are displayed below and can, once more, be downloaded by a click on the button. As before, the data is also saved in ```../data/processed/```.

```{r displayFirstRound}
# display data
gaechterFirstRound %>%
  head(n = 15) %>%
  kbl() %>% 
  # scroll_box(height = "200px") %>%
  kable_paper("hover", 
              full_width = TRUE,
              fixed_thead = TRUE)

# create download button
gaechterFirstRound %>%
      download_this(
        output_name = "gaechter2017_R1",
        output_extension = ".csv", # CSV output
        button_label = "Download csv",
        button_type = "default"
        )
```

# Outlook

Having replicated Gaechter et al.'s main figures (more or less) the next step is to prepare the data we obtain in our experiment for the analysis. This will be done in the second report using simulated data.^[Eventually, one can use that report and apply it to the actual data.]

>>>>

library(haven)
library(data.table)
library(magrittr)
library(kableExtra)
library(DescTools) # gini coefficient
library(downloadthis)
library(Rmisc)
library(ggplot2)
library(wesanderson)
```

@@

# Load Data

```{r readData}
DT <- read_dta(file="../data/gaechteretal/GMTV-data.dta") %>% data.table()
DT <- DT[order(treat, gr_id, per)]
```

# Calulate Variables

```{r calcVars}
DT[,
   gini2 := Gini(c(tokens, other1, other2, other3)),
   by = .(subj_id, per)]

DT[,
   mean2 := sum/gdp]
```

# Subset

```{r}
temp <- DT[exp_num == 5 | exp_num == 8 | exp_num == 9]
temp[order(gr_id, per),
         .(exp_num, gr_id, per, subj_id, # IDs
             tokens, other1, other2, other3, gdp, #endowments
             putin, pu1, pu2, pu3, sum, mean, mean2, # contributions
             gini, gini2)] %>% 
  head(n = 9) %>%
  kbl()
```
